Analysis of bulk void regions

### 2014-07-02 cosmic_voids.tex
Part of introduction and more references bibtex

Cosmic voids are one of the more striking features of the Mpc universe, 
where they are complementary to the filamentary 
\cite{Neyrinck08}

>>>>

Since voids where discovered in the first compiled galaxy surveys 
\citep{Chincarini75, Gregory78, Einasto80M, Einasto80N, Kirshner81, 
Kirshner87}, they have been identified as one of the most striking features 
of the Megaparsec universe, being a complementary aspect along with the 
filamentary and hierarchically clustered nature of the cosmic web 
\citep{Bond96}.
